---
title: "Mtcars Shiny Prediction Model - Reproducible Pitch"
author: "Amar Kotecha"
date: "29 April 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Project

The project involves two main parts:

1. Write a shiny application with associated documentation and deploy the application on Shiny's server.
2. Develop a presentation to pitch the app using RStudio Presenter. 

## App Overview

- The app is a prediction model based off the mtcars dataset contained within R
- A linear model is fit to the dataset to predict the efficiency of a car (mpg) using three variables:

1. Weight
2. Quarter mile time
3. Transmission


## Graphs - mpg against dependent variables

```{r cars, echo = FALSE, warning=FALSE, message=FALSE}
data("mtcars")
attach(mtcars)
par(mfrow=c(1,3))
plot(wt,mpg, main="Scatterplot of wt vs. mpg", data = mtcars)
plot(qsec,mpg, main="Scatterplot of qsec vs. mpg", data = mtcars)
boxplot(mpg~am, main="Boxplot of mpg by am (0=Auto, 1=Man)", data = mtcars)
```

## Links

The app has been published to the Shiny server and can be found here:

https://akotecha.shinyapps.io/Data_Products_Coursera/

The code and associated documentation can be found at the github repository:

https://github.com/akotecha/dataproductsweek4

